Consistency scores in text data

### 2020-08-04 outputs/documents/paper.Rmd
n-gram implementation write up

Language models underpinned by n-grams are widely applied in text prediction, spelling-correction, and machine translation (@brown1992class). In our application, we use a tri-gram based model to detect both real-word and non-word errors and correct them with the candidate word that has the highest probability. **(TODO: Add more about how we use n-gram once the functions in the app are in place.)**

However, n-gram models do not take the linguistic structure of language into account. For instance, @rosenfeld2000two [p. 1]  **(Ke-Li add page please)** discusses language in this context, saying that '...it may as well be a sequence of arbitrary symbols, with no deep structure, intention or thought behind'. The prediction of the next word is based on only a few preceding words and broader context is not taken into account. Hence next-word prediction using n-gram based language models can be limited.

**(Ke-Li add brief write-up of implementation in R please. Probably quanteda unless there's a better option.)**
The data set we used for training the n-gram model is [**(Ke-Li add a data set once settled the choice)**]. For generating n-grams, we used the Text Analysis Utilities (tau) R package to tokenize the training corpus into tri-grams.

@@

To illustrate the difference, consider the quote from Descartes, 'I think therefore I am'. The focus word for which we want to learn the embedding is 'therefore', and the context window is set to two. This means that we consider the two words immediately preceding and proceeding 'therefore'. The CBOW input is 'I, think, I, am', and the output is 'therefore'. In contrast, the continuous skip-gram input is 'therefore', while 'I, think, I, am' is the output. The input layer encodes terms within a context window to one-hot vectors. Using a projection matrix, the input layer is  projected to a projection layer and the features are. **(Ke-Li: Please fix this sentence.)** Finally, the output layer is a softmax regression classifier that obtains the posterior distribution of words (@rong2014word2vec). It is the input and output vectors that differ between the two architectures.

@@

**(Ke-Li add brief write-up of implementation in R please.)**

>>>>

Language models underpinned by n-grams are widely applied in text prediction, spelling-correction, and machine translation (@brown1992class). In our application, we use a tri-gram based model to detect both real-word and non-word errors and correct them with the candidate word that has the highest probability.

However, n-gram models do not take the linguistic structure of language into account. For instance, @rosenfeld2000two [p. 1] discusses language in this context, saying that '...it may as well be a sequence of arbitrary symbols, with no deep structure, intention or thought behind'. The prediction of the next word is based on only a few preceding words and broader context is not taken into account. Hence next-word prediction using n-gram based language models can be limited.

**(Ke-Li add brief write-up of implementation in R please. Probably quanteda unless there's a better option.)**
To implement the n-gram model, we used the Text Analysis Utilities (tau) R package to tokenize the training corpus (citation('tau')). To ensure that the three-word sequences are split within a sentence, we split the corpus into sentences by period, exponential mark, or question marks. We then manually added an end of sentence token $<s>$ to the end of each sentence. We used the textcnt() function turn the training corpus into tri-grams, and the function outputs a textcnt object that resembles a table object that has contains the tri-grams and their counts. We then removed all the tri-grams that contains an end-of-sentence token, so the tri-grams that include a word from a new sentence will be removed. For example, the tri-gram "day </s> we" will be removed because it has words from two different sentences. The following is the sample output that show the first 4 tokens:

```{r table1, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- " 
| there was no  | a rain so | a walk that | an hour in  | 
|---------------|-----------|-------------|-------------|
| 2             | 1         | 1           | 1           |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```
We can then access the tri-grams by calling the names of the object and use their counts to proceed to probability calculation. In calculating the probability of the tri-grams, we applied Kneser–Ney smoothing, the smoothing technique recommended by @chen1999empirical to improve the accuracy of n-gram models **(This function is written manually, but it's not my own code. I am reading about the Kneser–Ney smoothing to understand the math, will replace the function afterwards)**. Finally, we create a data table that contains the first two words and the last of each tri-gram in separate column and the smoothed probability in another column. The example row of the table is the following:

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- " 
| First Words   | Last Word | Probability |
|---------------|-----------|-------------|
| there was     | no        | 0.6278947   | 
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

@@

To illustrate the difference, consider the quote from Descartes, 'I think therefore I am'. The focus word for which we want to learn the embedding is 'therefore', and the context window is set to two. This means that we consider the two words immediately preceding and proceeding 'therefore'. The CBOW input is 'I, think, I, am', and the output is 'therefore'. In contrast, the continuous skip-gram input is 'therefore', while 'I, think, I, am' is the output. The input layer encodes terms within a context window to one-hot vectors. Using a projection matrix, the projection layer then project the discrete one-hot vectors to lower-dimension continuous vectors. Finally, the output layer is a softmax regression classifier that obtains the posterior distribution of words (@rong2014word2vec). It is the input and output vectors that differ between the two architectures.

@@

**(Ke-Li add brief write-up of implementation in R please.)**
#### Notes ####
CBOW might be better for text cleaning because it uses the context to predict the center word.
